MCC Simulations

### 2018-02-20 stats/simulations/mcc_simulations.Rmd
minor adjustment layout novel + pref

sum= ggarrange(mp,ip, cgp,seq,
          ncol = 1, nrow = 4,
          common.legend=TRUE)
```
```{r fig3, fig.asp = 1.2}
sum
```

@@

lm <- glmer(correct ~ speaker * prior * info+ (1|subid), 
      data = participant_data,
      family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

>>>>

sum= ggarrange(mp, cgp,ip,seq,
          ncol = 1, nrow = 4,
          common.legend=TRUE)
```
```{r fig3, fig.asp = 1.2}
sum
```

@@

lm <- glmer(correct3 ~ speaker * prior * info+ (1|subid), 
      data = participant_data,
      family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
